\pkg{ggenealogy}: An \proglang{R} Package for Visualizing Genealogical Data

### 2016-11-17 article.tex
multivariate animation in plotPathOnAll()

\begin{Code}
plotPath(pathTN, "devYear")
\end{Code}

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, "devYear", fontFace = 2) + ggplot2::xlab("Development Year")
\end{Code}

>>>>

\begin{Code}
plotPath(pathTN, sbGeneal, "devYear")
\end{Code}

@@

\begin{Code}
R> pathBZ <- getPath("Bedford", "Zane", sbIG, sbGeneal, "devYear")
R> plotPath(pathBZ, sbGeneal, "devYear", fontFace = 2) + ggplot2::xlab("Development Year")
\end{Code}
